### 2019-12-18 README.Rmd
Update readme, ready to open

The goal of zonebuilder is to ...

@@

You can install the released version of zonebuilder from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("zonebuilder")
```

And the development version from [GitHub](https://github.com/) with:

@@

## Example

```{r}
library(sf)
devtools::load_all()
plot(zb_region)
```

The aim is to be able to break up geographical space into discrete chunks.
The syntax is designed to be user friendly, e.g.:

```{r}
x = zb_region
q = zb_quadrat(x, 4) # break into 4
plot(q)
```

Or doughnuts

```{r}
plot(zb_doughnut(x, n = 4))
doughnut_4km = zb_doughnut(x, d = 4)
doughnut_4km
plot(sf::st_geometry(doughnut_4km))
plot(doughnut_4km[3, ], col = "blue", add = TRUE)
```

>>>>

The goal of zonebuilder is to break up large regions into manageable zones for research and applied transport planning, to support the global transition away from fossil fuels in the transport sector, and towards more healthy modes of transport like walking, cycling and renewable electricity-powered public transport.

@@

<!-- You can install the released version of zonebuilder from [CRAN](https://CRAN.R-project.org) with: -->

```{r, eval=FALSE, echo=FALSE}
install.packages("zonebuilder")
```

Install it from [GitHub](https://github.com/) with:

@@

## Using zonebuilder

Zonebuilder works with `sf` objects and works well alongside the `sf` package and visualisation packages that support spatial data such as `ggplot2`, `leaflet`, `mapdeck`, `mapview` and `tmap`, the last of which we'll use in the following maps.
Attaching the package provides the example dataset `zb_region`, the geographic boundary of a large city (London, UK):

```{r}
library(zonebuilder)
library(tmap)
tmap_border = tm_shape(zb_region) + tm_borders()
tmap_border
```

The core functions in the package break up geographical space into discrete chunks.
The syntax is designed to be user friendly.
The following command, for example, breaks London into quadrats of equal size (and keeping only the space inside the boundary):

```{r}
x = zb_region
q = zb_quadrat(x, ncol = 4) # break into 4
qtm(q) 
```

Another zoning option is 'doughnuts':

```{r}
tmap_arrange(
  qtm(zb_doughnut(x, n_circles = 3)) + tmap_border,
  qtm(zb_doughnut(x, distance = 3)) + tmap_border
)
```

A new zoning system implemented in the function `zb_zone()` segments doughnuts of gradually increasing width to create concentric segmented annuli (CSA):

```{r}
qtm(zb_zone(x))
```

This function gives you control over a number of parameters, as documented in the help pages and an in-progress academic paper.

```{r}
args(zb_zone)
```
